### 2021-06-03 paper/calibration_and_estimation.tex
Update work multiplier figure and add figure of rapid tests shares.

\begin{figure}[ht]
    \centering
    \includegraphics[width=1.1 \textwidth]{../figures/work_multiplier.png}
    \caption{Share of workers attending work normally.}
    \label{fig:work_multiplier}
    \figurenotes{
        The figure shows the percentage of pre-pandemic work mobility taking place
        since the start of the pandemic. In our model this is used as a proxy for the
        share of workers that attend work as usual. Workers are ordered with the
        importance of personal contacts for their work. Thus, if the share of
    }
\end{figure}

@@

>>>>

\begin{figure}[ht]
    \centering
    \includegraphics[width=1.1 \textwidth]{../figures/results/figures/work_multiplier_since_sep}
    \caption{Share of Workers with Work Contacts}
    \label{fig:work_multiplier}
    \figurenotes{The figure shows the work mobility as reported by \cite{Google2021}. We take this as a proxy of the share of workers who are not in home office, i.e. who still have physical work contacts.}
\end{figure}

@@

\begin{figure}[ht]
    \centering
    \caption{Share of Individuals Having Ever Done a Rapid Test}
    \label{fig:share_ever_rapid_test}
    \begin{subfigure}{.6\textwidth}
      \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/spring_fit/full_share_ever_rapid_test}
    \end{subfigure}%
    \begin{subfigure}{.6\textwidth}
      \includegraphics[width=0.9 \textwidth]{../figures/results/figures/scenario_comparisons/spring_fit/full_share_rapid_test_in_last_week}
    \end{subfigure}
    \caption{Share of Individuals Having Done a Rapid Test in the Last Week}
    \label{fig:explain_decline}
    \figurenotes{\textcolor{red}{\ldots}}
\end{figure}
